Aligning marine species range data to better serve science and conservation

### 2016-02-01 manuscript-main.Rmd
notes re: missing map pairs...

data_file <- 'data/spp_list_w_area_trimmed.csv'
spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE) %>%
#  filter(!is.na(popn_category)) %>% ### filter out unassessed species
  filter(!is.na(sm_perc))           ### filter out NA maps (usually IUCN maps with no polygons)

>>>>

data_file <- 'data/spp_list_w_area_trimmed.csv'
spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE)
### NOTE: as of 1/31, there are supposedly 2246 paired maps; but
### only 2003 unique IUCN species names in the maps list - presumably 
### the remainder are NA area (no polygons in LOICZID area)
